\bf A Hierarchical Model for Heterogenous Reliability Field Data

### 2018-03-31 paper/supplement.tex
Adds density plots of the prior distributions to the Supplemental Materials document

\pagebreak
\section{Posterior predictive graphical checks}
\item Full set of Figures 5 and 6 for all 44 drive-models.  Numbering in the top left indicates drive-model.  Left: Adjusted K-M estimates of the proportion failing.  The original data (bold line) and 19 ``replicated" data sets from the posterior predictive distribution (dashed lines) are shown.  Right: Posterior median of proportion failing as a function of time for Models 1-4.  Plotted on Weibull probability scales.  The solid step function is the adjusted K-M estimate.  
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-1.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-2}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-3.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-4.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-5.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-6.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-7.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-8.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-9.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-10.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-11.pdf}
\end{figure}
\clearpage

>>>>

\pagebreak
\section{Posterior predictive graphical checks}
Full set of Figures 5 and 6 for all 44 drive-models.  Numbering in the top left indicates drive-model.  Left: Adjusted K-M estimates of the proportion failing.  The original data (bold line) and 19 ``replicated" data sets from the posterior predictive distribution (dashed lines) are shown.  Right: Posterior median of proportion failing as a function of time for Models 1-4.  Plotted on Weibull probability scales.  The solid step function is the adjusted K-M estimate.  
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-1.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-2}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-3.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-4.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-5.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-6.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-7.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-8.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-9.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-10.pdf}
\end{figure}
\begin{figure}[H]
\includegraphics[width=\textwidth]{ppcheck-v2-11.pdf}
\end{figure}
\clearpage

\section{Density Plots for Prior Distributions}
To better visualize the prior distributions, below are plots of
the prior densities for Models 1 - 4.
\begin{figure}[H]
\center
\includegraphics[width=\textwidth]{priorsmod1.pdf}
\caption{Prior Densities for Model 1}
\end{figure}

\begin{figure}[H]
\center
\includegraphics[width=.7\textwidth]{priorsmod2.pdf}
\caption{Prior Densities for Model 2}
\end{figure}

\begin{figure}[H]
\center
\includegraphics[width=\textwidth]{priorsmod4.pdf}
\caption{Prior Densities for Models 3 and 4}
\end{figure}
